A simulation framework for exploring spatio-temporal dynamics in mixed fisheries

### 2018-01-31 write_up/mixfishsim_ecolmod.tex
manu updates

Fishing exploits spatio-temporally hetergenous fish populations without fully
selective gear which can result in unintended, unwanted catch of low quota or
protected species. Reducing these unwanted catches is crucial for biological
and economic sustainability of 'mixed fisheries'. \\

Understanding of spatio-temporal fishery dynamics is limited by a lack of full
understanding of population distribution and how fishers interact with the
different populations. We develop a spatio-temporal simulation model that
incorporate i) delay-difference population dynamics, ii) population movement
dynamics using Gaussian Random Fields, iii) fishery dynamics for multiple fleet
characteristics based on a correlated random walk and learned behaviour. \\

Using our model we simulation 20 years of exploitation of the fish populations
and use the results from the fishing model to draw inference on the underlying
population structures.  We compare this inference to i) a simulated fixed-site
sampling design commonly used for fisheries monitoring purposes, ii) the
underlying population structures input to the simulation.\\

We find that... \\

@@

Fishers exploit fish populations that are heterogenously distributed in space
and time without prior knowledge of species distributions and non-selective
fishing gear. Fisheries managed by single-species quotas catch an assemblage of
species, known as mixed fisheries, leading to discarding of overquota catch.
Reducing discarding is crucial to ensure biological and economic sustainability
of fisheries. As such there is increasing interest in technical solutions
such as gear, spatial closures as a way of avoiding discarding unwanted catch.
\\

Use of spatial management as a tool is hampered by lack of knowledge of fish
and fishery spatiotemporal dyanmics and understanding of the scale at which
processes are important for management. Understanding of the correct scale for
spatial management is crucial in order to implement measures at a resolution
that ensures effective management\cite{Dunn2016} while minimising economic
impact; for example a scale which promote species avoidance for vulnerable or
low quota species while allowing continance of sustainable fisheries for
available quota species. \\

Ensuring measures are implemented at an appropriate scale has been a challenge
in the a past that has led to ineffectual measures with unitended consequences
such as limited impact towards the management objective or increased benthic
impact on previously unexploited areas (e.g. the cod closure in the North
Sea\cite{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
information has become available through the combination of logbook and Vessel
Monitoring System (VMS) data\cite{Lee2010, Bastardie2010, Gerritsen2012,
	Mateo2016}, though such information is patchy and derived from an
inherently biased sampling programme (i.e. targeted fishing). Further,
generally fishers only recorded landings (not catch) on a daily basis. This
leads to questions about the validity of inferences that can be drawn from
landings data assigned to VMS activity pings. \\

@@

We develop a simulation model with a modular event-based approach, where
modules occur on independent time-scales appropriate to capture the
characteristic of the process modelled. The fishing model operated on a
tow-by-tow basis, while population dynamics (fishing and natural mortality,
growth) operate on a daily time-step.  Population movement occurs on a
two-weekly time-step, while recruitment occurs periodcally each year for a set
time period (e.g. 3 weeks) at at specified point individual to a species. The
model structure is summerised in Figure 1.\\

In the following section, we describe each of the model components; 1)
Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
fishery dynamics.\\

@@

\begin{equation*}
	\begin{split}
	B_{y,w+1} = &\\
	& (1 + \rho) B_{y,w} \cdot e^{-Z_{y,w}} - \rho \cdot e^{-Z_{y,w}} \hspace{2.9cm}
	\times \\  
	& (B_{y,w-1} \cdot e^{-Z_{y,w-1}} + Wt_{R-1} \cdot \alpha_{w-1} \cdot R_{\tilde{y}(y,w-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{w} \cdot R_{\tilde{y}(y,w)} 
	\end{split}
\end{equation*}

where $\rho$ is Brody's coefficient, shown to be approximately equal to
$exp(-K)$, where $K$ is the growth rate from a von bertalanffy logistic growth
model \cite{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{w}$ represents
the proportion of fish recruited during the week, while $R_{\tilde{y}}$ is the
annual recruits. \\

@@

\begin{equation*}
C_{w} = \frac{F_{w}}{F_{w}+M_{w}} * (1 - e^{-(F_{w} + M_{w})}) * B
\end{equation*}

@@

Recruitment is modelled through a function relating the biomass at time of
recruitment to recruits, either as a stochastic Beverton-Holt stock-recruit
form (\cite{Beverton1957}):

@@

In order to simulate how fish populations might be distributed in space and
time, we employed a Gaussian spatial process to model habitat suitability for
each of the populations, with an advection-diffusion process to control how the
populations moved in time. \\

@@

The specification of the covariance structure directly affects the smoothness
of the surfaces which the process generates.  We used the \textit{Matérn}
family of covariance structures, one where the correlation strength weakens the
further the distance apart (i.e. the correlation between $S(x)$ and $S(x')$
decreases as the distance $u = ||x - x'||$ increases).  The \textit{Matérn}
correlation is a two-parameter family where: \\

@@

The population is initialised at a single location, and subsequently moves
according to a probabilistic distribtion based on habitat suitability and
distance from current cell.

@@

Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$, and
$\lambda$ is some rate of decay.\\

@@

The fleet dynamics can be broadly categorised into three components; fleet
targeting - which determines the fleet catch efficiency and preference towards
a particular species; trip-level decisions, which determine the initial
location to be fished at the beginning of a trip; and within-trip decisions,
determining movement from one fishing spot to another within a trip.  A further
sub-model controls local depletion of fish populations at fished sites.

@@

Each fleet of \textit{n} vessels is characterised by both a general efficiency,
\textit{Q}, and a species specific efficiency, ${Q_{s}}$.  Thus, the product of
these parameters affects the overall catch rates for the fleet and the
preferential targeting of one species over another.  This, in combination with
the parameter choice for the step-function (as well as some randomness from the
exploratory fishing process) determines the preference of fishing locations for
the fleet.  All species prices are kept the same, across fleets, though can be
made to vary seasonally.

@@

Fishing locations within a trip are determined by a Random Walk process. A
Random walk was chosen as it is commonly used in ecology to describe animal
movement which searching for homogeneously distributed prey about which there
is uncertain knowledge. In a random walk, movement is a stochastic process
through a series of steps that can either be equal in length or take some other
functional form.  The direction of the random walk can be correlated, a
characteristic known as 'persistence', providing some overall location
directional movement \cite{Codling2008} or uncorrelated. \\

@@

We use a modified random walk where directional change is based on a correlated
circular distribution where a favourable fishing ground is likely to be "fished
back over" by the vessel returning in the direction it came from and step
length (i.e. the distance travelled from the current to the next fishing
location) is determined by relating recent fishing success, measured as the
summed value of fish caught, $$Rev = \sum_{s=1}^{\infty} C_{s} \cdot Pr_{s}$$
where $C_{s}$ is catch of a species, and $Pr_{s}$ price of a species, to step
distance. Here, when fishing is successful vessels remain in a similar location
and continue to exploit the local fishing grounds. When unsuccessful, they move
some distance away from the current fishing location. The movement distance
retains some degree of stochasticity, which can be controlled separately. \\

@@

with $k$ the concentration parameter from the von mises distribution which we
correlate with the revenue so that $k = (revenue + 1 / maxRevenue) * max_{k}$

where $max_{k}$ is the maximum concentration value, $k$, and maxRevenue is
parameterised as for $\beta_{3}$ in the step length function. \\

@@

Where several fishing vessels are exploiting the same fish population
competition is known to play an important role in local distribution of fishing
effort \cite{Gillis1998}. If several vessels are fishing on the same patch of
fish, local depletion and interference will affect fishing location choice of
the fleet as a whole \cite{Rijnsdorp2000, Poos2007a}. In order to account for
this behaviour, the fishing sub-model operates spatially on a daily time-step
so that for future days the biomass available to the fishery is reduced in the
areas fished. The cumulative effect is to make heavily fished areas less
attractive as future fishing opportunities. \\

@@

A fisheries-independent survey is simulated where fishing on a regular grid
begins each year at the same time for a given number of stations (a fixed
station survey design). Catches of the populations present are recorded but not
removed from the population. This provides a fishery independent snap shot of
the populations at a regular spatial distribution each year, similar to
scientific surveys undertaken by fisheries research agencies. \\

\section{Theory/calculation}

\textcolor{gray}{[Guidance: A Theory section should extend, not repeat, 
the background to the article already dealt with in the Introduction and lay
the foundation for further work.  In contrast, a Calculation section represents
a practical development from a theoretical basis.] \\}

@@

We set up with simulation to run for 20 years based on a 100 X 100 square grid,
with five fleets of 20 vessels each and four fish populations. Fishing takes
place four times a day per vessel and five days a week, while population
movement is every two weeks. \\

@@

We parameterised the simulation model for four populations with differing
habitat preference (Figure \ref{fig:1}) and defined two spawning areas for each
of the populations (Table \ref{tab:1}). \\

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
	Beverton-Holt Recruit $\sigma$ & 0.2 & 0.1 & 0.2 & 0.1 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Population dynamics and movement parameter settingSpawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

@@

The fleets were parameterised to reflect five different characteristics based
on targeting preference and exploitation dynamics (Table \ref{tab:2}). This
ensures that different fleets have different spatial dynamics, preferentially
targeted different fish populations. The stochasticity in the random walk
process ensures that different vessels within a fleet have slightly different
spatial distributions based on individual experience. \\

Each fleet was set so that, after the first year, fishing locations were chosen
based on experience built up in the same month from previous years and from
past trip fishing success. 'Success' in this context was defined as the
locations where the top 75 \% of revenue from previous trips was found. \\

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting}
\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences &&&& \\
	\hline
	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
	Price Pop3 & 600 & 600 & 600 & 600 & 600 \\
	Price Pop4 & 1600 & 1600 & 1600 & 1600 & 1600 \\
	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.02 & 0.02 \\
	$Q$ Pop2 & 0.02 & 0.01 & 0.01 & 0.01 & 0.01\\
	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.02 & 0.02 \\
	$Q$ Pop4 & 0.02 & 0.01 & 0.01 & 0.01 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 10 & 8 & 12 & 7 \\
	step function $\beta_3$ & MaxRev & MaxRev & MaxRev & MaxRev & MaxRev \\
	step function $rate$ & 10 & 20 & 15 & 25 & 10 \\
	Past Knowledge & T & T & T & T & T \\
	Past Year \& Month & T & T & T & T & T \\
	Past Trip & T & T & T & T & T \\
	Threshold & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}

@@

The survey simulation was set up with follow a fixed gridded station design
with 49 stations fished each year, starting on day 92 with same catchability
parameters for all populations (Q = 1). \\

@@

@@

textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
in a short Conclusions section, which may stand alone or form a subsection of a
Discussion or Results and Discussion section.]}

@@

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/annual_summary}
	\caption{Annual Summmary}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/fDynamics}
	\caption{f dynamics}
	\label{fig:3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_move}
	\caption{vessel movement}
	\label{fig:4}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_multi_move}
	\caption{vessel movement multi}
	\label{fig:5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_move_value}
	\caption{vessel movement value}
	\label{fig:6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/fleet_moves}
	\caption{fleet movement}
	\label{fig:7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/catch_comp}
	\caption{spatial catch composition}
	\label{fig:8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/catch_comp_clusters}
	\caption{spatial catch composition with clustering}
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/survey_index}
	\caption{survey index}
	\label{fig:10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/spatial_survey}
	\caption{survey spatial abundance}
	\label{fig:11}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/step_function}
	\caption{Realised step function}
	\label{fig:12}
\end{figure}

\newpage

@@

\newpage

>>>>

Fishing exploits spatio-temporally hetergenous fish populations without fully
selective gear which can result in unintended, unwanted catch of low quota or
protected species. Reducing these unwanted catches is crucial for biological
and economic sustainability of 'mixed fisheries' and implementation of an
ecosystem approach to fishing. \\

In order to implement effective spatial measures to reduce discards there needs
to be a good understanding of spatio-temporal fishery dynamics. However,
scientific advice is limited by a lack of knowledge of population distribution,
movement and how fishers interact with different fish populations. This is
because data on location of fish at high temporal and spatial resolutions is
expensive and difficult to collect and therefore proxy inferred from either
scientific survey or commercial catch data is often used to model
distributions, but often limited in its spatial or temporal resolution. \\

We develop a highly resolved spatio-temporal simulation model that incorporate
i) delay-difference population dynamics, ii) population movement dynamics using
Gaussian Random Fields to simulate patchy, hetergenously distributed
populations, iii) fishery dynamics for multiple fleet characteristics based on
a correlated random walk and learned behaviour. \\

Using our model we simulation 20 years of exploitation of the fish populations
and use the results from the fishing model to draw inference on the underlying
population structures. We compare this inference to i) a simulated fixed-site
sampling design commonly used for fisheries monitoring purposes, ii) the
underlying population structures input to the simulation, to establish whether
fishing dependent data, which is obtained from a biased sampling due to fishers
targeting, provides a robust picture of spatio-temporal distributions. [We
simulate a closure based on areas defined from commercial catch data and assess
its effectiveness on reducing catches of a fish population.] \\

We conclude that... \\

[233 words]

@@

Fishers exploit fish populations that are heterogenously distributed in space
and time without prior knowledge of species distributions using non-selective
fishing gear. Fisheries that catch an assemblage of species, known as mixed
fisheries, when managed by single-species quotas can end up discarding
overquota catch leading to overexploitation of fish populations. Reducing
discarding is crucial to ensure biological and economic sustainability of
fisheries and implementation of an ecosystem approach to fisheries. As such
there is increasing interest in technical solutions such as gear, spatial
closures as a way of avoiding discards.  \\

Use of spatial management as a tool has been proposed as a method to reduce
discards. However, its implementation is hampered by lack of knowledge of fish
and fishery spatiotemporal dyanmics and understanding of the scale at which
processes are important for management. Understanding of the correct scale for
spatial management is crucial in order to implement measures at a resolution
that ensures effective management\cite{Dunn2016} while minimising economic
impact; for example a scale which promote species avoidance for vulnerable or
low quota species while allowing continance of sustainable fisheries for
available quota species. \\

Ensuring measures are implemented at an appropriate scale has been a challenge
in the a past that has led to ineffectual measures with unitended consequences
such as limited impact towards the management objective or increased benthic
impact on previously unexploited areas (e.g. the cod closure in the North
Sea\cite{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
information has become available through the combination of logbook and Vessel
Monitoring System (VMS) data\cite{Lee2010, Bastardie2010, Gerritsen2012,
	Mateo2016} and more real-time spatial management has been able to be
implemented (e.g. \cite{Holmes2011}), though such information is patchy and
derived from an inherently biased sampling programme (i.e. targeted fishing).
Further, fishers generally only recorded landings (not catch) on a daily basis.
This leads to questions about the validity of inferences that can be drawn from
landings data assigned to VMS activity pings. \\

@@

We develop a simulation model with a modular event-based approach, where
modules are implemented on independent time-scales appropriate to capture the
characteristic of the process modelled. The fishing model operated on a
tow-by-tow basis, while population dynamics (fishing and natural mortality,
growth) operate on a daily time-step.  Population movement occurs on a
weekly time-step, while recruitment occurs periodcally each year for a set
time period (e.g. 3 weeks) at at specified point individual to a species. The
simulation framework is implemented in the statistical software package R
\cite{RCoreTeam2017}; available as an R package from the authors github
(\url{www.github.com/pdolder/MixFishSim}). The overall model structure is
summerised in Figure 1.\\

In the following section, we describe each of the model components; 1)
Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
fishery dynamics.

@@

\begin{equation*}
	\begin{split}
	B_{y,d+1} = &\\
	& (1 + \rho) B_{y,d} \cdot e^{-Z_{y,d}} - \rho \cdot e^{-Z_{y,d}} \hspace{2.9cm}
	\times \\  
	& (B_{y,d-1} \cdot e^{-Z_{y,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot R_{\tilde{y}(y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(y,d)} 
	\end{split}
\end{equation*}

where $\rho$ is Brody's coefficient, shown to be approximately equal to
$exp(-K)$, where $K$ is the growth rate from a von bertalanffy logistic growth
model \cite{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{d}$ represents
the proportion of fish recruited during that day for the year, while
$R_{\tilde{y}}$ is the annual recruits. \\

@@

\begin{equation*}
C_{d} = \frac{F_{d}}{F_{d}+M_{d}} * (1 - e^{-(F_{d} + M_{d})}) * B
\end{equation*}

@@

Recruitment is modelled through a function relating the biomass at time of
recruitment to recruits. In the simulation, it can be modelled either either as
a stochastic Beverton-Holt stock-recruit form (\cite{Beverton1957}):

@@

In order to simulate how fish populations might be distributed in space and
time, we employed a Gaussian spatial process to model habitat suitability for
each of the populations, with an advection-diffusion process to control how the
populations moved over time. \\

@@

The covariance structure affects the smoothness of the surfaces which the
process generates, and we used the \textit{Matérn} family of covariance
structures, one where the correlation strength weakens the further the distance
apart (i.e. the correlation between $S(x)$ and $S(x')$ decreases as the
distance $u = ||x - x'||$ increases).  The \textit{Matérn} correlation is a
two-parameter family where: \\

@@

In the simulation model, the habitat for each of the populations is generated
through the \textit{RFSimulate} function of the \textit{RandomFields} R package
\cite{Schlater2015}, implementing different parameter settings to affect the
patchiness of the populations. Each population is initialised at a single
location, and subsequently moves according to a probabilistic distribtion based
on habitat suitability and distance from current cell.

@@

Where $d_{AB}$ is the euclidean distance between cell $A$ and cell $B$, and
$\lambda$ is a given rate of decay.\\

@@

The fleet dynamics can be broadly categorised into three components; fleet
targeting - which determines the fleet catch efficiency and preference towards
a particular species; trip-level decisions, which determine the initial
location to be fished at the beginning of a trip; and within-trip decisions,
determining movement from one fishing spot to another within a trip.

@@

Each fleet of \textit{n} vessels is characterised by both a general efficiency,
\textit{Q}, and a population specific efficiency, ${Q_{p}}$.  Thus, the product
of these parameters affects the overall catch rates for the fleet and the
preferential targeting of one population over another. This, in combination
with the parameter choice for the step-function (as well as some randomness
from the exploratory fishing process) determines the preference of fishing
locations for the fleet.  All species prices are kept the same, across fleets,
though can be made to vary seasonally.

@@

Fishing locations within a trip are determined by a Random Walk process. A
Random walk was chosen as it is commonly used in ecology to describe animal
movement which searching for homogeneously distributed prey about which there
is uncertain knowledge. In a random walk, movement is a stochastic process
through a series of steps that can either be equal in length or take some other
functional form.  The direction of the random walk can be correlated, a
characteristic known as 'persistence', providing some overall location
of directional movement \cite{Codling2008} or uncorrelated. \\

@@

We use a modified random walk where directional change is based on a correlated
circular distribution where a favourable fishing ground is likely to be "fished
back over" by the vessel returning in the direction it came from and step
length (i.e. the distance travelled from the current to the next fishing
location) is determined by relating recent fishing success, measured as the
summed value of fish caught, $$Rev = \sum_{s=1}^{\infty} C_{s} \cdot Pr_{s}$$
where $C_{s}$ is catch of a species, and $Pr_{s}$ price of a species, to step
distance. Here, when fishing is successful vessels remain in a similar location
and continue to exploit the local fishing grounds. When unsuccessful, they move
some distance away from the current fishing location. The movement distance
retains some degree of stochasticity, which can be controlled separately.

@@

with $k$ the concentration parameter from the von mises distribution which we
correlate with the revenue so that $k = (Rev + 1 / RefRev) * max_{k}$,
where $max_{k}$ is the maximum concentration value, $k$, and RefRev is
parameterised as for $\beta_{3}$ in the step length function.

@@

Where several fishing vessels are exploiting the same fish population
competition is known to play an important role in local distribution of fishing
effort \cite{Gillis1998}. If several vessels are fishing on the same patch of
fish, local depletion and interference will affect fishing location choice of
the fleet as a whole \cite{Rijnsdorp2000, Poos2007a}. In order to account for
this behaviour, the fishing sub-model operates spatially on a daily time-step
so that for future days the biomass available to the fishery is reduced in the
areas fished. The cumulative effect is to make heavily fished areas less
attractive as future fishing opportunities.

@@

A fisheries-independent survey is simulated where fishing on a regular grid
begins each year at the same time for a given number of stations (a fixed
station survey design). Catches of the populations present are recorded but not
removed from the population. This provides a fishery independent snap shot of
the populations at a regular spatial distribution each year, similar to
scientific surveys undertaken by fisheries research agencies.

\section{Calculation}

\textcolor{gray}{[Guidance: A \underline{Theory} section should extend, not
repeat, the background to the article already dealt with in the	Introduction
and lay the foundation for further work.  In contrast, a
\underline{Calculation} section represents a practical development from a
theoretical basis.] \\}

@@

We set up with simulation to run for 20 years based on a 100 X 100 square grid,
with five fleets of 20 vessels each and four fish populations. Fishing takes
place four times a day per vessel and five days a week, while population
movement is every week.

@@

We parameterised the simulation model for four populations with differing
habitat preference (Figure \ref{fig:1}), population demographic and recruitment
functions; each of the populations also has two defined spawning areas and
movement rates (Table \ref{tab:1}). \\

@@

The fleets were parameterised to reflect five different characteristics based
on targeting preference and exploitation dynamics (Table \ref{tab:2}). This
ensures that different fleets have different spatial dynamics, preferentially
targeted different fish populations. The stochasticity in the random walk
process ensures that different vessels within a fleet have slightly different
spatial distributions based on individual experience, while the step function
was parameterised dynamically so that vessels take smaller steps where the
fishing location yields in the top X Quartile of the value available in that
year (as defined per fleet in Table \ref{tab:2}). \\

Each fleet was set so that, after the first year, fishing locations were chosen
based on experience built up in the same month from previous years and from
past trip fishing success. 'Success' in this context was defined as the
locations where the top 75 \% of revenue from was found in previous trips.

@@

The survey simulation was set up with follow a fixed gridded station design
with 49 stations fished each year, starting on day 92 with same catchability
parameters for all populations (Q = 1).

@@

Need to consider what best to present here as 4 / 5 figures:

\begin{itemize}
	\item Spatial dynamics: e.g. Figure 14. showing the population movement
		across weeks, including a spawning period.
	\item Overall population trends: e.g. Figure 3, showing the population
		dynamics at play.
	\item Realised step function: e.g. Figure 13, showing how the movement
		and turning angle responds. This could be combined with Figure
		7 for a more complete visualisaiton.
	\item Catch composition and spatial clustering: e.g. Figure 10, showing
		the importance of spatial resolution.
	\item Some measure of temporal trends/changes in spatial composition -
		could pick a certain cell and show how the proportions change
		over time ? An example is Figure 15, though there is little
		variation here. I think this is because the static habitat with
		population movement is far more stable than the previous
		directly affected population distributions (where there was an
		advective-diffusive process from the SPDE). Might need to
		consider how to change this?  Could include a spatio-temporally
		changing habitat suitability covariate, e.g. temperature ??
	\item Comparison of population structure from i) commercial sampling,
		ii) fisheries independent survey, iii) real population. This
		should be some statistical measure...not sure best approach
		here.
	\item [If we perform the closure, some measure of cost/benefit based on
		different resolutions of data and data used (i.e. commercial,
		survey, real populations). This could be on the basis of
		closing x cells, giving cell references to the model so they
		cannot be fished. Need to consider whether this is also a
		seasonal closure.]
\end{itemize}

@@

\textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
in a short Conclusions section, which may stand alone or form a subsection of a
Discussion or Results and Discussion section.]}

@@

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting}
\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences &&&& \\
	\hline
	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
	Price Pop3 & 600 & 600 & 600 & 600 & 600 \\
	Price Pop4 & 1600 & 1600 & 1600 & 1600 & 1600 \\
	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 10 & 8 & 12 & 7 \\
	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
	step function $rate$ & 10 & 20 & 15 & 25 & 10 \\
	Past Knowledge & T & T & T & T & T \\
	Past Year \& Month & T & T & T & T & T \\
	Past Trip & T & T & T & T & T \\
	Threshold & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/annual_summary}
	\caption{Summary of annualised metrics: biomass, catch, fishing
		mortality and recruitment. x-axis is the year, y the value}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/fDynamics}
	\caption{f dynamics - the daily fishing mortalities, each year is a
		different colour}
	\label{fig:3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_move}
	\caption{vessel movement - a single trip movement for one vessel}
	\label{fig:4}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_multi_move}
	\caption{vessel movement for multiple trips from a single vessel. Note
	the movement off the side pops up the other side, but is joined by a
	line across the grid. This is from the torus approach rather than the
	edges being barriers}
	\label{fig:5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_move_value}
	\caption{movement of a single vessel over a few trips overlaid on the
		value field (i.e. sum of the population abundance x catchability x value}
	\label{fig:6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/fleet_moves}
	\caption{An entire fleets (20 vessels) movement for a single trip}
	\label{fig:7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/catch_comp}
	\caption{spatial catch composition - the raw catches per cell at 4
		different spatial resolutions. Sorry, its a bit small at the
		moment!}
	\label{fig:8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/catch_comp_clusters}
	\caption{spatial catch composition (as above) but with clustering of
		cells performs on the bottom row. I'm confused as to why some
		entirely blue cells in the raw catch composition get allocated
	to the same cluster as some entirely red cells - needs investigating,
	it may be the clustering is not optimal}
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/survey_index}
	\caption{survey index - a non-spatial index generated from the fishery independent
	survey}
	\label{fig:10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/spatial_survey}
	\caption{survey spatial abundance - a bubble plot of the survey
		abundances, not really useful for the paper}
	\label{fig:11}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/step_function}
	\caption{Realised step function - the step function as realised for a
		single fleet. For turning angles, it can be seen that at higher
	values, the turning range is less}
	\label{fig:12}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/pop_dist}
	\caption{Spatial dynamics - the four populations at four time steps.
		Not really happy about the lack of dynamics here - mainly down
	to the static habitat leading to the populations settle in same cells
	over most time steps (exception: during the spawning period). Could
	include a temperature covariate or something to force some more
	temporal changes?}
	\label{fig:13}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/Proportion_in_cell}
	\caption{Temporal dynamics - the proportion of each population in a
		randomly chosen cell. Similar criticism as above}
	\label{fig:14}
\end{figure}

@@

\clearpage
